Hierarchy Builder: algebraic~hierarchies made easy in Coq with Elpi

### 2020-03-30 rebuttal.txt

Here the message I propose, it is ~600 words so there is space if you
want to write more:

Dear PC members, first of all we would like to thank the reviewers for
their valuable feedback. We believe we will be able to address all
their requests for the final version, namely clarify the exposition in
sections 4 and 5 (as per review 1 and 2), and add a few extra details
in section 6 (as per review 2).

Specific answer to reviewer 1
-----------------------------

- p4-5, evolution of the hierarchy:
     Could you make clearer the distinction (or absence of) between
     axioms and theorems in your implementation of a theory (problem
     mentioned on line 121). I.e., does it matter or not for the user
     of the hierarchy.

It does not matter: addrN is name he can use in her proofs. What
changed is how it is "implemented" by the hierarchy designer. Line
121 is very much related to the remark at lines 421-425, we shall
hint that in section 2 as well.

- Propositions 5 and 8: there is no proof, but is there anything to
prove?

We agree that 5 is a remark. On the contrary 8 shows M \subset F
by providing an implementation of requires, provides and from.
This proposition identifies *factories* as the central notion of HB,
since mixins are just a special case. Trivia: in an early draft the
name of the language was, indeed, Factory.

- Section 4:
     What are you describing here?
     Is it the code your tool generate?
     Does it correspond (exactly) to examples in Section 2?
     Has anything been omitted?

4.1 show Coq code that is equivalent to the HB commands issued
in Section 2.
HB commands do not synthesize that text, but have the same effect.

Many details were omitted. For example the abbreviations mentioned in
section 3.3 are not there. Another omission is that all "exported"
notions are gathered into an inner module, eg Monoid.Exports, etc.
We believe these details are not very interesting, but we will clarify
the status of the Coq code in section 4.

General answer to all reviewers
-------------------------------
All reviewers acknowledge that HB looks useful. Reviewer 1 flatters
us with "the tool is invaluable" and acknowledges that a contribution
of HB is "providing a way for normal Coq users to write hierarchies
using the packed class discipline". Reviewer 2 finds it "promising".
Reviewer 3 finds the machinery "impressive".

The main critic to HB, by Reviewer 3, is that it looks not only
impressive,
but also intimidating and Reviewer 3 wonders if a Coq user would run
the
risk of depending on HB in his work.

We use the remaining space to comment on that, that we believe is a
very pertinent remark.

In an early prototype of HB we considered generating text (Coq source
code).
We believe this approach could let users take advantage of HB without
depending on it (permanently). We do not provide this feature in the
current code because, honestly, it is not the most intriguing feature
to
implement or to describe in a paper.

We shall consider that feature again in the future, as an extreme
measure,
if the software stack behind HB turns out to severely hinder its
adoption.
We hope Reviewer 1 is right in saying that even regular Coq users could
be interested in using HB, and if the tool turns out to be popular its
maintenance will be assured by its authors and the community of users,
as it is the case for the Coq system or the Mathematical Components
library.

### 2020-03-30 rebuttal.txt

Dear PC members, first of all we would like to thank the reviewers for their
valuable feedback. We believe we will be able to address all their requests for
the final version, namely clarify the exposition in sections 4 and 5 (as per
review 1 and 2), and add a few extra details in section 6 (as per review 2).

Answer to reviewer 1
-----------------------------

- p4-5, evolution of the hierarchy:
         Could you make clearer the distinction (or absence of) between
         axioms and theorems in your implementation of a theory (problem
         mentioned on line 121). I.e., does it matter or not for the user
         of the hierarchy.

There are two distinct use cases for a hierarchy:
1. one assumes a structure as
     an hypothesis. In this case, all its axioms are theorems so the distinction
     axiom-theorem does not matter.
2. one instantiates a structure on a concrete
     type in order to access all its theory. Here, however, one must pick an
     axiomatic (i.e. a set of axioms) to show Coq that some type is indeed an
     instance of a structure. If for each structure there is only one axiomatic
     (which is its internal representation) and if we keep changing it, some theorems
     may become axioms and increase the burden on the user (this is what happens with
     addrC in V2, in order to instantiate a ring one has to prove it, while it was
     not required in V1). We fix that by letting the designer provide as many
     axiomatics as she wants, so that the user can pick the most convenient one, in
     particular V3 also provides the axiomatic from V1 as a factory. Behind the
     scenes, hierarchy-builder compiles it to the axiomatic currently used as the
     internal representation (made of mixins).

We plan to integrate a variation of the text above as the transition from
section 2.1 to 2.2.

- Propositions 5 and 8: there is no proof, but is there anything to
Prove?

Albeit trivial, they are both theorems. Our mistake was to mix the proof with
the statement.

Proposition 5) dep represents a transitively closed DAG, in particular
  dep*(dep*(M)) ⊆ dep*(M).
Proof.
dep is transitively closed since records are well typed in the empty context.
dep describes a DAG since Coq does not admit circular definitions.
Qed.

Proposition 8) There is a way to see mixins as factories (M ⊆  F).
Proof.
For each m ∈ M we pose
* requires(m) = dep(m)
* provides(m) = {m}
* from (m, m) = fun T (p : m T p σ ) (x : m T p 1 . . . p n ) => x ∈ B
Qed.

This proposition identifies *factories* as the central notion of HB, since
mixins are just a special case. Trivia: in an early draft the name of the
language was, indeed, Factory.

- Section 4:
         What are you describing here?
         Is it the code your tool generates?
         Does it correspond (exactly) to examples in Section 2?
         Has anything been omitted?

Section 4.1 shows Coq code that is equivalent to the HB commands given in
Section 2. These commands do not synthesize that text, but have the same effect.

Many details were omitted:
* the abbreviations mentioned in section 3.3
* the declarations of canonical structures are postponed to 4.3
* "Exported" notions are gathered into an inner module, eg Monoid.Exports.

We believe these details are not very interesting, but we will clarify the
status of the Coq code in section 4 in the final version.

Comment to all reviewers
-------------------------------

We could not avoid to remark that, by lack of clarity on our side, an important
aspect of HB was not sufficiently put forward. Indeed two reviewers write
seemingly opposite remarks:

* Reviewer 1 : "The first [contribution], surprisingly little advertised, [is]
     providing a way for normal Coq users to write hierarchies using the packed class
     discipline"

* Reviewer 3 :  “I can imagine a few experts using these tools to build
     hierarchies, but I would not expect the average Coq user to invest time into
     learning about them”.

We agree sections 4 and 5 of the paper can look intimidating to a non Coq +
Packed Classes expert, but these details are essentially the ones a user of HB
does not need to understand in order to use the tool. Indeed, the implementation
of HB takes care of these details and avoids most of the common mistakes one can
hardly avoid when writing Packed Classes code by hand. In the final version of
the paper, we intend to clarify this aspect in the introduction.

Finally, It is true that the software stack is large and may discourage the
adoption of HB, as remarked by Reviewer 3. In an early prototype of HB we
considered generating text (Coq source code). We believe this approach could let
users take advantage of HB without depending on it (permanently). We do not
provide this feature in the current code base because, honestly, it is not the
most intriguing feature to implement or to describe in a paper. We shall
consider that feature again in the future, as an extreme measure, if the
software stack behind HB turns out to severely hinder its adoption. However, we
hope Reviewer 1 is right in saying that the tool is invaluable, and if the tool
turns out to be popular its maintenance will be assured by its authors and the
community of users, as it is the case for the Coq system or the Mathematical
Components library.

### 2020-03-30 rebuttal.txt

Dear PC members, first of all we would like to thank the reviewers for their
valuable feedback. We believe we will be able to address all their requests for
the final version, namely clarify the exposition in sections 4 and 5 (as per
review 1 and 2), and add a few extra details in section 6 (as per review 2).

*Answer to reviewer 1*

- p4-5, evolution of the hierarchy: Could you make clearer the
  distinction (or absence of) between axioms and theorems in your
  implementation of a theory (problem mentioned on line 121). I.e.,
  does it matter or not for the user of the hierarchy.

There are two distinct use cases for a hierarchy:
1. one assumes a structure as an hypothesis. In this case, all its
   axioms are theorems so the distinction axiom-theorem does not
   matter.
2. one instantiates a structure on a concrete type in order to access
   all its theory. Here, however, one must pick an axiomatic (i.e. a
   set of axioms) to show Coq that some type is indeed an instance of
   a structure. If for each structure there is only one axiomatic
   (which is its internal representation) and if we keep changing it
   across versions, some theorems may become axioms and increase the
   burden on the user (this is what happens with addrC, in order to
   instantiate a ring in V2 one has to prove it, while it was not
   required in V1). We fix that by letting the designer provide as
   many axiomatics (i.e. factories) as she wants, so that the user can
   pick the most convenient one, in particular V3 also provides the
   axiomatic from V1. Behind the scenes, hierarchy-builder compiles it
   to the axiomatic currently used as the internal representation
   (made of mixins).

@@

Albeit trivial, they are both theorems. Our mistake was to mix the proof with
the statement. Here is the modification we will make:

Proposition 5) dep represents a transitively closed DAG, in particular
  dep*(dep*(M)) ⊆ dep*(M).
Proof.
dep is transitively closed since records are well typed in the empty context.
dep describes a DAG since Coq does not admit circular definitions.
Qed.

Proposition 8) There is a way to see mixins as factories (M ⊆  F).
Proof.
For each m ∈ M we pose
* requires(m) = dep(m)
* provides(m) = {m}
* from (m, m) = fun T (p : m T p σ ) (x : m T p 1 . . . p n ) => x ∈ B
Qed.

The latter proposition identifies *factories* as the central notion of
HB, since mixins are just a special case. Trivia: in an early draft
the name of the language was, indeed, Factory.

@@

- Section 4: What are you describing here?  Is it the code your tool
  generates?  Does it correspond (exactly) to examples in Section 2?
  Has anything been omitted?

Section 4.1 shows Coq code that is almost equivalent to the HB commands given in
Section 2. These commands do not synthesize that text, but have the same effect.

Many details were omitted:
- the abbreviations mentioned in section 3.3
- the declarations of canonical structures are postponed to 4.3
- "Exported" notions are gathered into an inner module, e.g. Monoid.Exports.

We believe these details are not very interesting, and we will clarify the
status of the Coq code in section 4 in the final version.

*Comment to all reviewers*

We could not avoid to remark that, by lack of clarity on our side, an important
aspect of HB was not sufficiently put forward. Indeed two reviewers write
seemingly opposite remarks:
- Reviewer 1 : "The first [contribution], surprisingly little
   advertised, [is] providing a way for normal Coq users to write
   hierarchies using the packed class discipline"
- Reviewer 3 : “I can imagine a few experts using these tools to build
   hierarchies, but I would not expect the average Coq user to invest
   time into learning about them”.

### 2020-03-31 rebuttal.txt

Dear PC members, first of all we would like to thank the reviewers for their
valuable feedback. We believe we will be able to address all their requests for
the final version, namely clarify the exposition in sections 4 and 5 (as per
review 1 and 2), and add a few extra details in section 6 (as per review 2).

*Answer to reviewer 1*

> p4-5, evolution of the hierarchy:
> Could you make clearer the distinction (or absence of) between
> axioms and theorems in your implementation of a theory (problem
> mentioned on line 121). I.e., does it matter or not for the user of
> the hierarchy.

@@

There are two distinct use cases for a hierarchy:
1. one assumes a structure as an hypothesis. In this case, all its
   axioms are theorems so the distinction axiom-theorem does not
   matter.
2. one instantiates a structure on a concrete type in order to access
   all its theory. Here, however, one must pick an axiomatic (i.e. a
   set of axioms) to show Coq that some type is indeed an instance of
   a structure. If for each structure there is only one axiomatic
   (which is its internal representation) and if we keep changing it
   across versions, some theorems may become axioms and increase the
   burden on the user (this is what happens with addrC, in order to
   instantiate a ring in V2 one has to prove it, while it was not
   required in V1). We fix that by letting the designer provide as
   many axiomatics (i.e. factories) as she wants, so that the user can
   pick the most convenient one, in particular V3 also provides the
   axiomatic from V1. Behind the scenes, hierarchy-builder compiles it
   to the axiomatic currently used as the internal representation
   (made of mixins).

We plan to integrate a variation of the text above as the transition from
section 2.1 to 2.2.

> Propositions 5 and 8: there is no proof, but is there anything to Prove?

@@

Proposition 5) dep represents a transitively closed DAG, in particular
  dep*(dep*(M)) ⊆ dep*(M).
Proof.
dep is transitively closed since records are well typed in the empty context.
dep describes a DAG since Coq does not admit circular definitions.
Qed.

Proposition 8) There is a way to see mixins as factories (M ⊆  F).
Proof.
For each m ∈ M we pose
* requires(m) = dep(m)
* provides(m) = {m}
* from (m, m) = fun T (p : m T p σ ) (x : m T p 1 . . . p n ) => x ∈ B
Qed.

The latter proposition identifies *factories* as the central notion of
HB, since mixins are just a special case. Trivia: in an early draft
the name of the language was, indeed, Factory.

> Section 4:
> What are you describing here?
> Is it the code your tool generate?
> Does it correspond (exactly) to examples in Section 2?
> Has anything been omitted?

### 2020-04-17 hb.tex
all items for =ET= except the one on section 5 are done

The hierarchy of the Mathematical Components library
is implemented following the discipline of Packed Classes initially introduced
in \cite{DBLP:conf/tphol/GarillotGMR09} and later also adopted in
\cite{DBLP:conf/mpc/AffeldtNS19} and \cite{DBLP:journals/mics/BoldoLM15}.
We call Packed Classes a discipline, and not a language, because, in spite of
its many virtues, it is unwieldy to use. In particular it leaks to the user
many of the technical details of the Coq system. As a result, one
needs to be a Coq expert in order to build or modify a hierarchy, and even
experts make mistakes as shown in~\cite{KSdraft}.
Another inconvenience of the Packed Classes discipline is that even
simple changes to the hierarchy, such as splitting a structure into
two simpler ones, break user code.

@@

We use the \coq{Monoid_of_Type.Build} \emph{\phantterm{}}
(line~\ref{demo:theory:z:monoid:axioms})
in order to build an instance of the \coq{Monoid}
structure for binary integers \coq{Z}.
We then register that monoid instance as the canonical one on \coq{Z}
(line~\ref{demo:theory:z:monoid:canonical}) via the command
\coq{hb.canonical}.
We can similarly declare that \coq{Z} forms a ring by using
the \coq{Ring_of_Monoid.Build} \phantterm{}
(lines~\ref{demo:theory:z:ring:axioms} and~\ref{demo:theory:z:ring:canonical}).
Note that the \coq{Ring_of_Monoid.Build} \phantterm{} is not
a plain record constructor for \coq{Ring_of_Monoid}, since that
would require more arguments, namely the monoid ones (see the \coq{_}
at line~\ref{demo:theory:z:ring:axioms}). The
\phantterm{} synthesized by \HB{} infers them automatically
(as in~\cite[Section 7]{DBLP:conf/itp/MahboubiT13}) thanks to the \hbinstance{}
declaration given just above.

@@

Some operations and properties were moved from the old \mixin{} for rings
into a newborn \mixin{} \coq{AbelianGroup_of_Monoid} that gathers the
axioms needed to turn a monoid into an Abelian group. Consequently the \mixin{}
for rings is now called \coq{Ring_of_AbelianGroup} (instead of \coq{Ring_of_Monoid})
since it expects the type \coq{A} to be already an Abelian group and hence
gathers fewer axioms. \\
While operations moved from one structure to another, some properties
undergo a deep change in their status.
The lemma \coq{addrC} part of the abstract theory of
rings is now an axiom of Abelian groups, while \coq{addrN} is no more
an axiom of rings, but rather a theorem of the abstract theory of Abelian
groups.

With this new version of the hierarchy, that we name V2, code written
for version V1 breaks. For example the declaration of the canonical ring over
the integers fails, if only
because we do not have a \coq{Ring_of_Monoid.Build} \phantterm{} anymore.

@@

\begin{figure}[!h]
  \begin{center}
    \includegraphics[width=0.8\textwidth]{puzzle.pdf}
  \end{center}
  \caption{\label{fig:puzzle}The evolution of the hierarchy. V3 is backward compatible with V1, while V2 is not.}
\end{figure}

@@

\begin{wrapfigure}[3]{r}{.4\textwidth}
 \includegraphics[width=.4\textwidth]{v4.pdf}
 \caption{V4 introduces multiple inheritance. For brevity we omit the factories/builders for the upper arrows.}
 \label{fig:puzzle_v4}
\end{wrapfigure}
\
\begin{coqcode}
#\hbmixin{}# Record SemiRing_of_Monoid A 
    of Monoid A := {
  one : A;
  mul : A -> A -> A;
  (* 7 axioms are omitted. *)
}.

#\hbfactory{}# Record Ring_of_AbelianGroup A
    of AbelianGroup A := {
  (* 2 operators and 5 axioms are omitted. *)
}.
#\hbbuilders{}# Context A (a : Ring_of_AbelianGroup A).
..
#\hbend{}#.
\end{coqcode}

@@

Note that the binder \elpi{s\} at line \ref{binder:sort} lets one mention
the first field in the type of the second.
The syntax \elpi{{{ Type }}} is a quotation: it lets
one use the syntax of Coq to write an Elpi expression of type \elpi{term}.
The API \elpi{coq.CS.canonical-projections} lets us find the projections
automatically generated by Coq for a given record.
The last detail worth mentioning is that this program makes no use of
backtraking: the \elpi{std.do!} combinator signals that.

@@

In~\cite{CaretteCombinators} Carette and O'Connor describe the language of
Theory Presentation Combinators that can be used to describe a hierarchy of
algebraic structures.
They focus on the categorical semantics of the language that is built upon
the category of context.
They do not describe any actual compilation to the language of a mainstream
interactive prover, indeed they claim their language to be mostly type theory
independent. We know they considered targeting type theory and the language
of unification hints~\cite{10.1007/978-3-642-03359-9_8}
(a super set of the one of Canonical Structures),
but we could not find any written trace of that. Language wise they provides
keywords such as \verb+combine+ and \verb+over+ to share (reuse) a property
when defining a new structure. For example in order to avoid restating
the commutativity property when defining Abelian groups they combine
a commutative monoid and a group forcing the subjacent monoid to coincide: %
\verb-CommutativeGroup := combine CommutativeMonoid , Group over Monoid.-
In our language \HB{} the same role is played by \emph{\mixins{}}.
A \mixin{} lets one write once and for all a property and abstract it over types
and operations so that it can be reused in all the structures that need it.
One operation \HB{} allows for but that does not seem to be possible in the
setting of Presentation Combinators is the one of replacing an axioms with a
lemma and vice versa. As shown in \autoref{subsec:evolution} \HB{} supports
that.

>>>>

The hierarchy of the Mathematical Components library
is implemented following the discipline of Packed Classes initially introduced
by Garillot, Gonthier, Mahboubi and Rideau~\cite{DBLP:conf/tphol/GarillotGMR09}
and later also adopted by Affeldt, Nowak, and Saikawain
to describe a hierarchy of monadic effects~\cite{DBLP:conf/mpc/AffeldtNS19}
and by Boldo, Lelay, and Melquiond in the Coquelicot library of real
analysis~\cite{DBLP:journals/mics/BoldoLM15}.
We call Packed Classes a discipline, and not a language, because, in spite of
its many virtues, it is unwieldy to use. In particular it leaks to the user
many of the technical details of the Coq system. As a result, one
needs to be a Coq expert in order to build or modify a hierarchy, and even
experts make mistakes as shown in~\cite{KSdraft}.
Another inconvenience of the Packed Classes discipline is that even
simple changes to the hierarchy, such as splitting a structure into
two simpler ones, break user code.

@@

We use the \coq{Monoid_of_Type.Build} \emph{\phantterm{}}
(line~\ref{demo:theory:z:monoid:axioms})
in order to build an instance of the \coq{Monoid}
structure for binary integers \coq{Z}.
We then register that monoid instance as the canonical one on \coq{Z}
(line~\ref{demo:theory:z:monoid:canonical}) via the command
\coq{HB.instance}.
We can similarly declare that \coq{Z} forms a ring by using
the \coq{Ring_of_Monoid.Build} \phantterm{}
(lines~\ref{demo:theory:z:ring:axioms} and~\ref{demo:theory:z:ring:canonical}).
Note that the \coq{Ring_of_Monoid.Build} \phantterm{} is not
a plain record constructor for \coq{Ring_of_Monoid}, since that
would require more arguments, namely the monoid ones (see the \coq{_}
at line~\ref{demo:theory:z:ring:axioms}). The
\phantterm{} synthesized by \HB{} infers them automatically
(as in~\cite[Section 7]{DBLP:conf/itp/MahboubiT13}) thanks to the \hbinstance{}
declaration given just above.

@@

Some operations and properties were moved from the old \mixin{} for rings
into a newborn \mixin{} \coq{AbelianGroup_of_Monoid} that gathers the
axioms needed to turn a monoid into an Abelian group. Consequently the \mixin{}
for rings is now called \coq{Ring_of_AbelianGroup} (instead of \coq{Ring_of_Monoid})
since it expects the type \coq{A} to be already an Abelian group and hence
gathers fewer axioms.
While operations moved from one structure to another, some properties
undergo a deep change in their status.
The lemma \coq{addrC} part of the abstract theory of
rings is now an axiom of Abelian groups, while \coq{addrN} is no more
an axiom of rings, but rather a theorem of the abstract theory of Abelian
groups proved at line~\ref{demo2:proof:addrN}.

It is worth clarifying here what axioms and lemmas are by looking at the
two distinct use cases for a hierarchy: 1) develop the abstract theory of some
structure; 2) apply the abstract theory on some concrete example.
In the first case
all the axioms of the structure are (assumed to be) theorems so the distinction
between axiom and theorem does not matter. This is what happens
in the proof of \coq{addNr} by taking \coq{R} to be of type
\coq{AbelianGroup.type} as an assumption.
In the second case,
in order to show Coq that a data type and some operations for a structure,
one must pick the axioms of the structure an prove them for that specific
type and operations. For example the \coq{Ring_of_Monoid.Build} \phantterm{}
is used at page~\pageref{demo:theory:z:ring:axioms} to package the set
of proofs that make \coq{Z} a ring (proviso \coq{Z} is already a monoid).

With this new version of the hierarchy, that we name V2, the axiomatic that
was previously exposed to user changed, and indeed
code written for version V1 breaks. For example the declaration of the
canonical ring over the integers fails, if only
because we do not have a \coq{Ring_of_Monoid.Build} \phantterm{}
anymore.

@@

\begin{figure}[!h]
  \begin{center}
    \includegraphics[width=\textwidth]{puzzle.pdf}
  \end{center}
  \caption{\label{fig:puzzle}The evolution of the hierarchy. V3 is backward compatible with V1, while V2 is not.}
\end{figure}

@@

\begin{coqcode}
#\hbmixin{}# Record SemiRing_of_Monoid A of Monoid A := {
  one : A;
  mul : A -> A -> A;
  (* 7 axioms are omitted. *)
}.
\end{coqcode}

\begin{wrapfigure}[3]{r}{.4\textwidth}
  \includegraphics[width=.4\textwidth]{v4.pdf}
  \caption{V4 introduces multiple inheritance. For brevity we omit the factories/builders for the upper arrows.}
  \label{fig:puzzle_v4}
\end{wrapfigure}
\
\begin{coqcode}
#\hbfactory{}# Record Ring_of_AbelianGroup A
  of AbelianGroup A := {
  (* 2 operators and 5 axioms are omitted. *)
}.
#\hbbuilders{}# Context A (a : Ring_of_AbelianGroup A).
..
#\hbend{}#.
\end{coqcode}

@@

Note that the binder \elpi{s\} at line \ref{binder:sort} lets one mention
the first field in the type of the second.
The syntax \elpi{{{ Type }}} is a quotation: it lets
one use the syntax of Coq to write an Elpi expression of type \elpi{term}.
The API \elpi{coq.CS.canonical-projections} lets us find the projections
automatically generated by Coq for a given record.
The last detail worth mentioning is that this program makes no use of
backtracking: the \elpi{std.do!} combinator signals that.

@@

In~\cite{CaretteCombinators} Carette and O'Connor describe the language of
Theory Presentation Combinators that can be used to describe a hierarchy of
algebraic structures.
They focus on the categorical semantics of the language that is built upon
the category of context.
They do not describe any actual compilation to the language of a mainstream
interactive prover, indeed they claim their language to be mostly type theory
independent. We know they considered targeting type theory and the language
of unification hints~\cite{10.1007/978-3-642-03359-9_8}
(a superset of the one of Canonical Structures),
but we could not find any written trace of that. Language-wise they provide
keywords such as \verb+combine+ and \verb+over+ to share (reuse) a property
when defining a new structure. For example in order to avoid restating
the commutativity property when defining Abelian groups they combine
a commutative monoid and a group forcing the subjacent monoid to coincide: %
\verb-CommutativeGroup := combine CommutativeMonoid , Group over Monoid.-
In our language \HB{} the same role is played by \emph{\mixins{}}.
A \mixin{} lets one write once and for all a property and abstract it over types
and operations so that it can be reused in all the structures that need it.
One operation \HB{} allows for but that does not seem to be possible in the
setting of Presentation Combinators is the one of replacing an axiom with a
lemma and vice versa. As shown in \autoref{subsec:evolution} \HB{} supports
that.
